\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-10 paper/ms.tex
Write about the code

The posterior distribution
\begin{align}
p(\params | \data) &= \frac{p(\params)p(\data | \params)}{p(\data)}\\
&= \frac{\pi(\params)L(\params)}{Z}
\end{align}

@@

%\section{Basic usage of DNest4}

%\section{Advanced usage}

@@

%\section{Implementing models}

@@

\begin{CodeChunk}
\begin{CodeInput}
void StraightLine::from_prior(RNG& rng)
{
   // Naive diffuse prior
   m = 1E3*rng.randn();
   b = 1E3*rng.randn();

@@

>>>>

In very compact notation, the posterior
posterior distribution for parameters $\params$ given data $\data$, within
context $I$, is
\begin{align}
p(\params | \data, I) &=
\frac{p(\params | I)p(\data | \params, I)}{p(\data | I)}
\end{align}
or
\begin{align}
\textnormal{posterior} &=
\frac{\textnormal{prior} \times \textnormal{likelihood}}
     {\textnormal{marginal likelihood}}.
\end{align}
When discussing computational matters, the prior is
often written $\pi(\theta)$, the likelihood $L(\theta)$,
and the marginal likelihood $Z$.

@@

\section{Basic usage of DNest4}
The

\section{Advanced usage}

@@

\section{Implementing models}

@@

\begin{CodeChunk}
\begin{CodeInput}
void StraightLine::from_prior(DNest4::RNG\& rng)
{
   // Naive diffuse prior
   m = 1E3*rng.randn();
   b = 1E3*rng.randn();

@@

This generates $m$, $b$, and $\sigma$ from their joint prior. In this case,
the priors are all independent, so this reduces to generating the parameters
each from their own prior distribution. For convenience, the \code{RNG} object
has \code{rand()} and \code{randn()} member functions to generate from
a Uniform$(0,1)$ and Normal$(0,1)$ distribution respectively.

The \code{perturb} member function is:

When implementing a model class, it is imperative that the
\code{from\_prior(DNest4::RNG\&)} and \code{perturb(DNest4::RNG\&)}
member functions be consistent with each other.
